---
title: "Generative Models for Classification"
subtitle: "IS382 - Predictive Modeling"
author: Jason Bryer, Ph.D.
# date: "September 28, 2026"
output:
  xaringan::moon_reader:
    css: ["assets/mtheme_max.css", "assets/fonts_mtheme_max.css"]
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: solarized-light
      highlightLanguage: R
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
    includes:
      in_header: [assets/header.html]
      after_body: [assets/insert-logo.html]
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# Cartoons from https://github.com/allisonhorst/stats-illustrations
# dplyr based upon https://allisonhorst.shinyapps.io/dplyr-learnr/#section-welcome

source('../config.R')

library(gganimate)
library(magick)
library(cowplot)
library(DT)
source('../R/roc.R')
# library(titanic)
# data("titanic")
library(VisualStats)
# library(VisualMLE)

```

class: center, middle, inverse, title-slide

# `r metadata$title`
## `r metadata$subtitle`
### `r metadata$author`
### `r metadata$date`



---
# Linear Discriminant Analysis








---
class: left, font140
# One Minute Paper

.pull-left[
1. What was the most important thing you learned during this class?
2. What important question remains unanswered for you?
]
.pull-right[
```{r, echo=FALSE, fig.width=5, fig.height=5}
omp_link <- get_omp_link(
	course = course,
	semester = paste0(semester, year),
	topic = 'Generative Models for Classification'
)
qrcode::qr_code(omp_link) |> plot(col = c('#FAFAFA', 'black'))
```
.center[.font50[[Scan the QR code or click here to  
complete the One Minute Paper](`r omp_link`)]]
]
